Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix grammar.
Fix grammar: subject/verb agreement

Then the application was tested was by loading the initial cluster
creation landing page in a browser tab. Nodes were randomly added to
the cluster (by clicking on the link embedded in the page) or removed
from the cluster (by closing a tab). After each change the steady
state properties were checked.

@@

The results of the manual testing above showed that Raft over WebRTC
was able to perform leader elections correctly, the log and state
machine was replicated correctly to all nodes, and the safety
properties were maintained. During testing the membership of the
cluster was changed numerous times (both node additions and removals)
and the Raft properties were maintained throughout. In addition,
client interaction was tested to make sure commands were still
properly added to the state machine and transaction log.

>>>>

Then the application was tested by loading the initial cluster
creation landing page in a browser tab. Nodes were randomly added to
the cluster (by clicking on the link embedded in the page) or removed
from the cluster (by closing a tab). After each change the steady
state properties were checked.

@@

The results of the manual testing above showed that Raft over WebRTC
was able to perform leader elections correctly, the log and state
machine were replicated correctly to all nodes, and the safety
properties were maintained. During testing the membership of the
cluster was changed numerous times (both node additions and removals)
and the Raft properties were maintained throughout. In addition,
client interaction was tested to make sure commands were still
properly added to the state machine and transaction log.
